\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-01-10 paper.qmd
Add summary for PBMC and Mouse data sets

@@

>>>>

MSE_df_pbmc <- read_rds("data/pbmc/summary_pbmc.rds")

## To draw with AIC
aic_plot_pbmc <- ggplot(MSE_df_pbmc |> dplyr::filter(data_type == "training"), aes(x = number_of_bins,
                                                                                 y = total_error,
                                                                                 color = method
)) +
  geom_point() +
  geom_line() +
  #geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  #annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=-5000, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  theme_light() +
  theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  scale_color_discrete_qualitative() +
  ylab("AIC") +
  xlab("Total number of bins")
## Effective number of bins along x-axis

mse_plot_pbmc <- ggplot(MSE_df_pbmc, aes(x = number_of_bins,
                                       y = total_mse,
                                       color = method
)) +
  geom_point() +
  geom_line() +
  theme_light() +
  theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  # geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  # annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=0.25, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  scale_color_discrete_qualitative() +
  ylab("MSE") +
  xlab("Total number of bins")

```{r}
#| echo: false
#| fig-cap: The .
#| label: fig-diagnosticpltPBMC
#| out-width: 100%

aic_plot_pbmc + mse_plot_pbmc +
  plot_annotation(tag_levels = 'a') +
  plot_layout(guides='collect', ncol = 2) &
  theme(legend.position='bottom', plot.tag = element_text(size = 8))
```

@@

MSE_df_zei <- read_rds("data/zeisel/summary_zei.rds")

## To draw with AIC
aic_plot_zei <- ggplot(MSE_df_zei |> dplyr::filter(data_type == "training"), aes(x = number_of_bins,
                                                                                 y = total_error,
                                                                                 color = method
)) +
  geom_point() +
  geom_line() +
  #geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  #annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=-5000, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  theme_light() +
  theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  scale_color_discrete_qualitative() +
  ylab("AIC") +
  xlab("Total number of bins")
## Effective number of bins along x-axis

mse_plot_zei <- ggplot(MSE_df_zei, aes(x = number_of_bins,
                                       y = total_mse,
                                       color = method
)) +
  geom_point() +
  geom_line() +
  theme_light() +
  theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title = element_text(size = 7),
        axis.text = element_text(size = 7)) +
  # geom_vline(xintercept = NROW(full_grid_with_hexbin_id)) +
  # annotate("text", x= (NROW(full_grid_with_hexbin_id) - 10), y=0.25, label=paste0("effective number of bins = ", as.character(NROW(full_grid_with_hexbin_id))), angle=90) +
  scale_color_discrete_qualitative() +
  ylab("MSE") +
  xlab("Total number of bins")

```{r}
#| echo: false
#| fig-cap: The .
#| label: fig-diagnosticpltZEI
#| out-width: 100%

aic_plot_zei + mse_plot_zei +
  plot_annotation(tag_levels = 'a') +
  plot_layout(guides='collect', ncol = 2) &
  theme(legend.position='bottom', plot.tag = element_text(size = 8))
```

### 2024-01-10 paper.tex
Add summary for PBMC and Mouse data sets

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, breakable, sharp corners, borderline west={3pt}{0pt}{shadecolor}, enhanced, boxrule=0pt, interior hidden]}{\end{tcolorbox}}\fi

@@

@@

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, enhanced, breakable, interior hidden, frame hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners]}{\end{tcolorbox}}\fi

@@

{\centering \includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-diagnosticpltPBMC-1.pdf}

\caption{\label{fig-diagnosticpltPBMC}The .}

@@

{\centering \includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-diagnosticpltZEI-1.pdf}

\caption{\label{fig-diagnosticpltZEI}The .}
